% UCL Thesis LaTeX Template
%  (c) Ian Kirker, 2014
% 
% This is a template/skeleton for PhD/MPhil/MRes theses.
%
% It uses a rather split-up file structure because this tends to
%  work well for large, complex documents.
% We suggest using one file per chapter, but you may wish to use more
%  or fewer separate files than that.
% We've also separated out various bits of configuration into their
%  own files, to keep everything neat.
% Note that the \input command just streams in whatever file you give
%  it, while the \include command adds a page break, and does some
%  extra organisation to make compilation faster. Note that you can't
%  use \include inside an \include-d file.
% We suggest using \input for settings and configuration files that
%  you always want to use, and \include for each section of content.
% If you do that, it also means you can use the \includeonly statement
%  to only compile up the section you're currently interested in.
% You might also want to put figures into their own files to be \input.

% For more information on \input and \include, see:
%  http://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include


% Formatting rules for theses are here: 
%  http://www.ucl.ac.uk/current-students/research_degrees/thesis_formatting
% Binding and submitting guidelines are here:
%  http://www.ucl.ac.uk/current-students/research_degrees/thesis_binding_submission

% This package goes first and foremost, because it checks all 
%  your syntax for mistakes and some old-fashioned LaTeX commands.
% Note that normally you should load your documentclass before 
%  packages, because some packages change behaviour based on
%  your document settings.
% Also, for those confused by the RequirePackage here vs usepackage
%  elsewhere, usepackage cannot be used before the documentclass
%  command, while RequirePackage can. That's the only functional
%  difference.
\RequirePackage[l2tabu, orthodox]{nag}


% ------ Main document class specification ------
% The draft option here prevents images being inserted,
%  and adds chunky black bars to boxes that are exceeding 
%  the page width (to show that they are).
% The oneside option can optionally be replaced by twoside if
%  you intend to print double-sided. Note that this is
%  *specifically permitted* by the UCL thesis formatting
%  guidelines.
%
% Valid options in terms of type are:
%  phd
%  mres
%  mphil
%\documentclass[12pt,phd,draft,a4paper,oneside]{ucl_thesis}
\documentclass[12pt,phd,a4paper,oneside]{ucl_thesis}


% Package configuration:
%  LaTeX uses "packages" to add extra commands and features.
%  There are quite a few useful ones, so we've put them in a 
%   separate file.
\input{MainPackages}

% Sets up links within your document, for e.g. contents page entries
%  and references, and also PDF metadata.
% You should edit this!
\input{LinksAndMetadata}

% And then some settings in separate files.
\input{FloatSettings} % For things like figures and tables
\input{BibSettings}   % For bibliographies

% Title Settings
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\title{Optimization and Guess-then-Solve Attacks in Cryptanalysis}
\author{Guangyan Song}
\department{Department of Computer Science}


\begin{document}



\nobibliography*
% This is a dumb trick that works with the bibentry package to let
%  you put bibliography entries whereever you like.
% I used this to put references to papers a chapter's work was 
%  published in at the end of that chapter.
% For more information, see: http://stefaanlippens.net/bibentry

% If you haven't finished making your full BibTex file yet, you
%  might find this useful -- it'll just replace all your
%  citations with little superscript notes.
% Uncomment to use.
%\renewcommand{\cite}[1]{\emph{\textsuperscript{[#1]}}}

% At last, content! Remember filenames are case-sensitive and 
%  *must not* include spaces.
\include{Preamble}
\chapter*{List of Publications}
\begin{itemize}
	\item Courtois, N.T., Gawinecki, J.A. and Song, G., 2012. Contradiction immunity and guess-then-determine attacks on GOST. Tatra Mountains Mathematical Publications, 53(1), pp.65-79. 
	\item Courtois, N., Mourouzis, T., Song, G., Sepehrdad, P. and Susil, P., 2014. Combined algebraic and truncated differential cryptanalysis on reduced-round Simon. In Proceedings of the 11th International Conference on Security and Cryptography, pp. 399-404. 
	\item Courtois, N.T., Mourouzis, T., Misztal, M., Quisquater, J.J. and Song, G., 2015. Can GOST Be Made Secure Against Differential Cryptanalysis?. Cryptologia, 39(2), pp.145-156. 
	\item Mourouzis, T., Song, G., Courtois, N. and Christofii, M., 2015. Advanced differential cryptanalysis of reduced-round simon64/128 using large-round statistical distinguishers. Cryptology ePrint Archive, Report 2015/481
	\item Nicolas Courtois, Guangyan Song, Ryan Castellucci:
	Speed Optimizations in Bitcoin Key Recovery Attacks, will appear in journal post-proceedings of CECC 2016,
	Central European Conference on Cryptology, Tatra Mountains Mathematic
	Publications.
	\item Courtois N., Sepehrdad P., Song G. and Papapanagiotakis-Bousy I. 2016. Predicting Outcomes of ElimLin Attack on Lightweight Block Cipher Simon. International Conference on Security and Cryptography pp. 465-470.
\end{itemize}
\chapter*{List of Software Deliverables}
\begin{itemize}
	\item  N Courtois, T Mourouzis, G Song. Simonspeck. \url{https://github.com/GSongHashrate/ SimonSpeck}
	NSA Simon and Speck C++ implementation, equation generator for all versions of Simon cipher.
	\item Nicolas Courtois, Jason Papapanagiotakis, Guangyan Song, Chris Park:
	"Fast Bitcoin data mining Tutorial" (used in GA18 and GA12 teaching/projects at University College London)
	\url{http://www.nicolascourtois.com/bitcoin/fast_bitcoin_data_mining.pdf}
	\item DeepElimLin: 
	``Java tool for DEEP INSPECTION of equations generated with ElimLin over GF(2)
	in Cryptalanalysis of Block Ciphers'', developed by Guangyan Song and Nicolas Courtois.
	Available at:
	\url{http://www.cryptosystem.net/aes/tools.html}
	\item How to crack bitcoin passwords at a very high speed: brainflayer cracker.
	\url{https://github.com/ryancdotorg/brainflayer} written by Ryan Castellucci. Nicolas
	Courtois and Guangyan Song contributed the code in ec\_pubkey\_fast.c
	which more than doubles the speed of public key computations. 
	
	\item How to crack bitcoin and LinkedIn passwords at home 
	(easy starter project for UCL students and GA18 code breaking competition, 
	by Nicolas Courtois and Guangyan Song. Cf. 
	\url{https://drive.google.com/open?id=0B0iephZbbC3uSU9WRUdWZVZfa1U}
	and database files \url{https://drive.google.com/file/d/0B0iephZbbC3uWERlanN5b3hJak0}. 
\end{itemize}

\include{Introduction}
\include{Chapter2}
\include{Chapter3}
\include{Chapter4}
\include{Chapter5}
\include{Chapter6}
\include{chapter8}
\include{Chapter7}

\include{Conclusions}
\include{Appendices} 
% You could separate these out into different files if you have
%  particularly large appendices.

% This line manually adds the Bibliography to the table of contents.
% The fact that \include is the last thing before this ensures that it
% is on a clear page, and adding it like this means that it doesn't
% get a chapter or appendix number.
\addcontentsline{toc}{chapter}{Bibliography}

% Actually generates your bibliography.
%\bibliographystyle{apa}
\bibliographystyle{abbrv}
\bibliography{PhD}

% All done. \o/
\end{document}
